Scalar and Representative Observables for Polarimetric SAR Data

### 2013-10-12 paper_dev/article.tex
updated change ratio plots, before merging with Ian's changes

@@

\begin{abstract}
%Problem statement  
This paper proposes a scalar and representative observable for the multi-dimensional POLSAR data,
  from which statistically consistent discrimination measures can be derived.
%What actually were done? and As the result, what is learned?
Specifically, the statistical behaviour of the POLSAR covariance matrix determinant is used
  to derive a scalar and generic statistical model for the multi-dimensional POLSAR data,
  which is specifically applicable to the two and three dimensional versions of partial and full monostatic polarimetric SAR data.
As the POLSAR covariance matrix determinant generalizes the SAR intensity towards the multidimensional extension,
  the proposed model is also shown to include the traditional model used for SAR intensity under its natural coverage.
%What are the larger implications of the findings presented in this paper?
Consequently, the main beneficial implication of the proposed approach is that
  it provides a consistent theory unifying the currently disconnected proposals for SAR and POLSAR discrimination measures
  which enables the adaptation of many existing SAR data processing techniques for POLSAR data.
%  it enables the adaptation of many existing SAR data processing techniques for POLSAR data,
%  and at the same time, it provides a consistent theory unifying the seemingly disparate discrimination measure proposals for SAR and POLSAR data.
\end{abstract}

@@

%What is the situation, the background context of your research? the BIG problem!
During the past decades, exponential growth in computing power has allowed the once computationally-demanding Synthetic Aperture Radar (SAR)
technology to become a feasible and preferred technique for earth observation applications.
SAR technology has since been extended in a few directions, one of which is the polarimetric SAR (POLSAR).
POLSAR extends SAR by exploiting the natural polarization property of Electro-Magnetic (EM) waves,
  leading to the availability of multi-channel POLSAR data, compared to traditional one-channel SAR data.

%Research Motivation: Why it is important to solve this problem?
%The POLSAR data, however, is multidimensional and stochastic.
Similar to the SAR data, the POLSAR data is stochastic.
Moreover, it is multi-dimensional making it even harder to interpret.
Under this context, it is therefore important to establish a simple and intuitive understanding of the data
  and statistical models are undoubtedly crucial in understand the stochastic its nature.
While several multidimensional models have been proposed for the POLSAR data (TODO:CITE source thesis),
  unfortunately, due to the multidimensional nature, they are complex and not very intuitive.
Practical POLSAR data processing, however, makes heavily use of scalar discrimination measures,
  which should be based on statistically consistent models for scalar and representative observables of the multidimensional data.
It is thus important to establish a scalar and representative observable for this multi-dimensional POLSAR data.

@@

%How do others solve this problem?
%The complex POLSAR data have been statistically modelled as following the complex Wishart distribution,
%  which apparently is multidimensional, complex and thus not very intuitive.
There has been a few scalar observables with accompanying statistical models proposal for POLSAR \cite{Conradsen_2003_TGRS_4, Alberga_2008_IJRS_4129, Joughin_1994_TGRS_562, Lee_1994_TGRS_1017, Touzi_1996_TGRS_519, Lopez-Martinez_2003_TGRS_2232, Erten_2012_Sensors_2766},
  but none of them is able to provide meaningful scalar discrimination measures.
%  but none of them has led to scalar discrimination measures proposal.
As such no observable has been widely accepted as being highly representative of the multi-dimensional data,
  which severely limits their applicability in practical data processing applications.
From an alternative approach, there are also a few POLSAR discrimination measures proposed,
  but all of them are based on the likelihood ratio statistics.
This statistical test should be based on an exact and consistent statistical distribution
  but so far has only shown to be based on an asymptotic distribution.

%Research Objective: Give your precise problem statement  
This article hence present a scalar and representative observable, and its associated generic statistical model,
  for the multi-dimensional POLSAR data that provides a consistent foundation for the derivation of POLSAR discrimination measures.
%Now State your approach  
%This study started off with the observation that the determinant of the covariance matrix is widely used in POLSAR discrimination measures.
%However, our survey of existing scalar models for POLSAR indicates that no statistical model for this observable has been published so far.
%Consequently, in this article, the statistical behaviour of the determinant of POLSAR covariance matrix is further investigated.
%Prof Vuns: comment: the article provides the result, not the journey!
The POLSAR data have been statistically modelled as following the complex Wishart distribution.
Consequently, the generic statistical model for the covariance matrix determinant, being just a scalar projection of the multidimensional data, is presented.
This model is then used to derive several scalar and consistent statistical models suggesting that their associated observables are capable of being used as discrimination measures for POLSAR data.
The specific two and three dimensional models of these models, 
  which also include the derived discrimination measures,
  are originally designed against both partial and full polarimetric SAR data.

%The specific two and three dimensional models are then validated against both partial and full polarimetric SAR data.
Interestingly the paper also shows that %It is also shown that
  the specific one dimensional versions of these models proposed 
  match perfectly with the traditional statistical model used for SAR intensity.
This effectively puts the one dimensional SAR theory to stay within the proposed scalar approach for multi dimensional POLSAR.
With this new insight the different discrimination proposals for SAR and POLSAR are reviewed and it is shown that the approach proposed in this paper provides a strong, unifying and consistent foundation relating them all together.
The applicability of these theoretical models is illustrated by experiments where the specific one, two and three dimensional versions of the proposed generic models are validated against practical data. 
%Furthermore, the approach proposed in this paper
%  not only provides a consistent foundation for the different discrimination measures proposal in POLSAR
%  but also leads to the establishment of a new discriminating measures: the determinant-ratio and the change-ratio.

@@

%Article Organization: Show that you deliver on the objectives and hence solve the stated problem
Thus, the rest of this article is organized as follows.
After the next section reviews existing discrimination measures as well as scalar observables models for POLSAR, section \ref{sec:theoretical_model}
  derives the generic statistical model for the determinant of the POLSAR covariance matrix
  and proposes several new discrimination measures for the multi-dimensional data.
After section \ref{sec:sar_special_case_of_polsar} illustrates the match between the specific model of one dimensional and the traditional model for SAR intensity,
  section \ref{sec:link_sar_polsar} links the disparate discrimination measure proposals for the traditional SAR and the more recent POLSAR data.
%Section \ref{sec:polsar_models_validation} then validates the specific one, two and three dimensional versions of the proposed model against real-life captured data.
The applicability of these models against practical data is illustrated in section \ref{sec:polsar_models_validation}.
Section \ref{sec:discussion} presents a high-level discussion of the results presented before
  section \ref{sec:conclusion} finally concludes this paper.

@@

%This section outlines related publication.
Section \ref{sec:lit_models} reviews various statistical models used for different scalar observables for POLSAR.
  where it is shown that none of these is able to provide statistically consistent discrimination measures. 
Section \ref{sec:lit_measures} further strengthens those findings by discussing discrimination measures that have been proposed for POLSAR,
  and it demonstrates that almost all of them are based on the likelihood statistical test for complex Wishart distribution.
While an exact statistical distribution is expected for the test,
  only asymptotic distribution is used in the original work \cite{Conradsen_2003_TGRS_4}.

@@

The commonly used measure of distance for matrices are either the Euclidean or Manhattan distances, defined respectively as:
\begin{align}
  d(C_x,C_y) &= \sum_{i,j} |\mathbb{R} (C_x - C_y)_{i,j}| + \sum_{i,j} |\mathbb{I} (C_x - C_y)_{i,j}| \\
  d(C_x,C_y) &= \sqrt{\sum_{i,j} |C_x - C_y|_{i,j}^2 }
\end{align}
where $C_{i,j}$ denotes the (i,j) elements of the POLSAR covariance matrix C,
 $||$ denotes absolute values
and $\mathbb{R},\mathbb{I}$ denote the real and imaginary parts respectively.
However, in the context of POLSAR, % covariance matrix
  these dissimilarity measures are not widely used 
  mainly due to the multiplicative nature of the noisy data.

@@

Taking the log-transformation of the above equation, and denote $C_{vx} = Z_x / L_x$, $C_{vy} = Z_y / L_y$ and $C_{vxy} = (Z_x + Z_y)/(L_x + L_y)$ then:
{\small
\begin{align}
  Q &= \frac{|C_{vx}|^{L_x} \cdot |C_{vy}|^{L_y} }{|C_{vxy}|^{L_x + L_y}} \label{eqn:ori_likelyhood_stats} \\
  \ln Q &= L_x \ln |C_{vx}| + L_y \ln |C_{vy}| - (L_x + L_y) \ln |C_{vxy}| \label{eqn:log_likelyhood_stats}
\end{align}
}

@@

%In this section, the generic scalar statistical model for POLSAR is presented.
In this section, after the basic foundations of POLSAR statistical analysis is introduced,
  the generic scalar statistical model for the multi-dimensional POLSAR is presented.
%  this section presents the theoretical model for multi-dimensional POLSAR data.

@@

Moreover, since the average and variance of these chi-squared distributions %and log-chi-squared distribution
  are known to be constant, i.e. $avg \left[ \chi(2L) \right] = 2L$ and $var \left[ \chi(2L) \right] = 4L$,
  the product and summation of these random variables also has fixed summary statistics.
Specifically:
{\footnotesize
\begin{align*}
  avg \left[ \prod^{d-1}_{i=0} \chi(2L-2i) \right] &= 2^d \cdot \prod^{d-1}_{i=0} (L-i), \\
  var \left[ \prod^{d-1}_{i=0} \chi(2L-2i) \right] &= \prod^{d-1}_{i=0} 4(L-i)(L-i+1) - \prod^{d-1}_{i=0} 4(L-i)^2, %\\
%  avg \left[ \sum^{d-1}_{i=0} \Lambda(2L-2i) \right] &= d \cdot \ln{2} + \sum^{d-1}_{i=0} \psi^0(L-i), \\
%  var \left[ \sum^{d-1}_{i=0} \Lambda(2L-2i) \right] &= \sum^{d-1}_{i=0} \psi^1(L-i)
\end{align*}
}

@@

%Assuming, on the one hand,
For cases where the true value of the underlying signal $\Sigma_v$ is known \textit{a priori},
then the determinant-ratio of the signal random variable ($\mathbb{R}_{\Sigma}$) %and log-distance ($\mathbb{L}$)
%  are observable according to the following definitions:
  is defined as:
%Eqns. \ref{eqn:prod_chi_squared_rv} and \ref{eqn:sum_log_chi_squared_rv} lead straight to the definition of the following random variables, which is the :
\begin{eqnarray}
  \mathbb{R}_{\Sigma} &=& \frac{|C_v|}{|\Sigma_v|} \label{eqn:determinant_ratio_observables}%\\
%  \mathbb{L} &=& \ln|C_v| - \ln|\Sigma_v| \label{eqn:log_distance_observables} 
\end{eqnarray}
%On the other hand, under a looser assumption %From another perspective
For cases where the POLSAR data is known to have come from a homogeneous area, but the true value of the underlying signal $\Sigma_v$ is \textit{unknown},
 then random variable called the change-ratio ($\mathbb{R}_{C}$)  is defined as:
\begin{eqnarray}
  \mathbb{R}_{C} &=& \frac{|C_1|}{|C_2|} \label{eqn:determinant_ratio_samples_observables}%\\
%  \mathbb{L} &=& \ln|C_v| - \ln|\Sigma_v| \label{eqn:log_distance_observables} 
\end{eqnarray}
where $C_1$ and $C_2$ are samples of the covariance matrix determinant in an assumed homogeneous area.

@@

Since each elementary component follows fixed distributions (i.e. $\chi^2(2L)$),
  it is natural that this variable also follows fixed distributions.
Moreover, it is independent of the underlying signal $\Sigma_v$,
  indicating its statistically consistent properties and hence its applicability as a POLSAR discrimination measure.
This claim is extrapolated from the widely-used intensity-ratio as SAR discrimination measure
  and will be further discussed in the next sections.
%is further strengthened in the next section which shows that the generic models for POLSAR presented in this paper also include the commonly-used models for SAR as its special 1-dimensional case. 
%This result shows how
%In short, these random variables are shown to follow consistent and fixed distributions,
%  regardless of the underlying signal $\Sigma_v$.

@@

%The previous sections have introduced and validated the theoretical models for 3-dimensional ($d=3$) full polarimetric and 2-dimensional ($d=2$) partial polarimetry, cases.
This section shows that the proposed generic model is equally  applicable to the 1-dimensional ($d=1$) case,
  which is physically equivalent to  collapsing the multi-dimensional POLSAR dataset  into conventional single dimensional SAR data.
Mathematically, the sample covariance matrix $C_v$ is reduced to the sample variance while the determinant $|C_v|$ is equivalent to  the scalar variance value.
As variance is equal to intensity $I$ for SAR data, our result is consistent with previous results for SAR intensity data.
Hence this derivation can be considered
  both as cross-validation for the proposed POLSAR model
  as well as evidence showing that
    the proposed generic model for POLSAR also includes the traditional model for SAR intensity in its natural coverage.
%  as well as reminding us that SAR is a special case of POLSAR.

@@

Since the PDF of chi-squared distribution can be written as:
\begin{align*}
\chi(2L) \sim pdf \left[ \frac{\chi^{L-1}e^{-\chi/2}}{2^L\Gamma(L)} \right]
\end{align*}
, applying variable change theorem into the above equations results in:
\begin{align*}
  |C_v| &\sim  pdf \left[ \frac{L^L x^{L-1} e^{-Lx/|\Sigma_v|}}{\Gamma(L) |\Sigma_v|^L} \right] \\ %\label{eqn:determinant_distribution} %\\
  \mathbb{R}_{\Sigma} = \frac{|C_v|}{|\Sigma_v|} &\sim pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx}}{ \Gamma(L)} \right] \\ %\label{eqn:polsar_ratio_det_cov_dist} \\
  \mathbb{R}_{C} = \frac{C_1}{C_2} &\sim pdf \left[ \frac{\Gamma(2L-1) x^{L-1}}{\Gamma^2(L-1) (1+x)^{2L}} \right]
\end{align*}
These equations match exactly with the following traditional model for multi-look SAR intensity:
  \begin{eqnarray}
I &\sim& pdf \left[ \frac{L^L x^{L-1} e^{-Lx/\bar{I}}}{\Gamma(L) \bar{I}^L} \right] \\
\mathbb{R}_{\bar{I}} = \frac{I}{\bar{I}} &\sim& pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx}}{ \Gamma(L)} \label{eqn:multi_look_SAR_ratio_dist} \right] \\
  \mathbb{R}_{I} = \frac{I_1}{I_2} &\sim& pdf \left[ \frac{\Gamma(2L-1) x^{L-1}}{\Gamma^2(L-1) (1+x)^{2L}} \right]
  \end{eqnarray}
considering that $|C_v| \mapsto I$ and $|\Sigma_v| \mapsto \bar{I}$ as multi-dimensional POLSAR collapses into single-dimensional SAR.

@@

Statistical models have always been the foundation to derive discrimination measures.
This is true for both fields of SAR and POLSAR.
For SAR, where the field is more or less settled on the issue,
  the statistical model for SAR intensity has been used to derive the most widely used intensity-ratio discrimination measure \cite{Rignot_1993_TGRS_896}.
For POLSAR, where the field is much less matured,
  the same case should apply, 
  except that so far only asymptotic distribution has been derived for the most common foundation, i.e. the likelihood test statistics \cite{Conradsen_2003_TGRS_4}.

@@

As for the first matter, in view of the models given in Eqn \ref{eqn:determinant_distribution},
  the likelihood test statistics presented in \cite{Conradsen_2003_TGRS_4} and rewritten in Eqns \ref{eqn:ori_likelyhood_stats} \& \ref{eqn:log_likelyhood_stats}
can be expressed as:
\begin{align*}
  \ln{Q} &\sim  k + L_x \Lambda^d_{L_x} + L_y \Lambda^d_{L_y} - (L_x + L_y) \Lambda^d_{(L_x + L_y)} \\
  Q &\sim e^k \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y}}{(\chi^d_{L_x + L_y})^{L_x + L_y}}   
\end{align*}
where $k = d \left[ (L_x + L_y) \ln(L_x + L_y) - L_x \ln{L_x} - L_y \ln{L_y} \right]$.
This, in essence, derives an exact statistical distribution for the likelyhood test statistics,
  as opposed to the asymptotic distribution derived in \cite{{Conradsen_2003_TGRS_4}}.

@@

Since it has been shown in Section \ref{sec:sar_special_case_of_polsar} that the model for the case of $d=1$ matches exactly with the traditional model for SAR intensity,
  the validation of the proposed $d=1$ model is quite straightforward. %only a simple validation is presented for this case.  
Fig. \ref{fig:verify_POLSAR_model_1D} presents the results of a test performed for the stated purpose.
In the test, the intensity of single-channel SAR data (HH) for a homogeneous area in both the AIRSAR Flevoland dataset is extracted.
The histograms for both the intensity and intensity ratio %the log-distance and contrast
  are then plotted against the theoretical PDF given above.
Also presented are the plots of the same test applied on a homogeneous patch inside the nine-look processed RADARSAT2 image.
The plots are obtained with ENL set an estimated value obtained using the technique presented in \cite{Anfinsen_2009_TGRS_3795}.
In all cases, good visual match is apparent, which hence validates the model proposed above. %providing us a simple validation of the result.

>>>>

\usepackage{graphicx}
\usepackage{pstricks}

\def\row{10}
\def\column{10}

\usepackage{xcolor}
\definecolor{plot}{rgb}{1,0.652,0.1705}

\newsavebox\IBox
\savebox\IBox{\includegraphics[width=1.5in,height=1.5in]{../images/verify_change_ratio_model_on_RADARSAT2_3d.eps}}

\psset
{
  xunit=\dimexpr\wd\IBox/\column,
  yunit=\dimexpr\ht\IBox/\row,
}

\newcommand{\plotWithLegend}[1]{          
          \begin{pspicture}[showgrid=false](\column,\row)% set showgrid=false for the final
	    \rput[bl](0,0){\includegraphics[width=1.5in,height=1.5in]{#1}}% \usebox\IBoxCRThreeR
	    \rput(5,1.5){\footnotesize{change-ratio}}
	    \rput{90}(1.5,5){\footnotesize{pdf/histogram}}
	    \psline[linecolor=plot](5,8)(6,8)
	    \psline[linestyle=dashed](5,9)(6,9)%another line style: dotted
	    \rput(8,8){\footnotesize{model}}
	    \rput(8,9){\footnotesize{data}}            
          \end{pspicture}
}

@@

\begin{abstract}
%Problem statement  
This paper proposes a scalar and representative observable for multi-dimensional POLSAR data,
  from which statistically consistent discrimination measures can be derived.
%What actually were done? and As the result, what is learned?
Specifically, the statistical behaviour of the POLSAR covariance matrix determinant is used
  to derive a scalar and generic statistical model for multi-dimensional POLSAR data,
  which is specifically applicable to the two and three dimensional versions of partial and full monostatic polarimetric SAR data.
As the POLSAR covariance matrix determinant generalizes the SAR intensity towards the multidimensional extension,
  the proposed model is also shown to include the traditional model of SAR intensity under its natural coverage.
%What are the larger implications of the findings presented in this paper?
Consequently, the main beneficial implication of the proposed approach is that
  it provides a consistent theory unifying the currently disconnected proposals for SAR and POLSAR discrimination measures
  which simplifies the adaptation of existing SAR data processing techniques for POLSAR data.
%  it enables the adaptation of many existing SAR data processing techniques for POLSAR data,
%  and at the same time, it provides a consistent theory unifying the seemingly disparate discrimination measure proposals for SAR and POLSAR data.
\end{abstract}

@@

%What is the situation, the background context of your research? the BIG problem!
During the past decades, exponential growth in computing power has allowed the once computationally-demanding Synthetic Aperture Radar (SAR)
technology to become a feasible and preferred technique for earth observation applications.
SAR technology has since been extended in a few directions, one of which is polarimetric SAR (POLSAR).
POLSAR extends SAR by exploiting the natural polarization property of Electro-Magnetic (EM) waves,
  leading to the availability of multi-channel POLSAR data, compared to traditional one-channel SAR data.

%Research Motivation: Why it is important to solve this problem?
%The POLSAR data, however, is multidimensional and stochastic.
Like SAR data, POLSAR data is stochastic.
Moreover, it is multi-dimensional, making it even harder to interpret.
Under this context, it is therefore important to establish a simple and intuitive understanding of the data.
 Statistical models are undoubtedly crucial in understanding its stochastic nature.
While several %multidimensional 
models have been proposed to describe POLSAR data, they
  unfortunately tend to be complex and not very intuitive due to the multidimensional nature of the data.
Practical POLSAR data processing however, makes heavy use of scalar discrimination measures,
  which should be based on statistically consistent models for scalar and representative observables of the multidimensional data.
It is thus important to establish a scalar and representative observable for this multi-dimensional POLSAR data.

@@

%How do others solve this problem?
%The complex POLSAR data have been statistically modelled as following the complex Wishart distribution,
%  which apparently is multidimensional, complex and thus not very intuitive.
There has been a few scalar observables with accompanying statistical models proposal for POLSAR \cite{Conradsen_2003_TGRS_4, Alberga_2008_IJRS_4129, Joughin_1994_TGRS_562, Lee_1994_TGRS_1017, Touzi_1996_TGRS_519, Lopez-Martinez_2003_TGRS_2232, Erten_2012_Sensors_2766},
  but none of them is able to provide meaningful scalar discrimination measures.
%  but none of them has led to scalar discrimination measures proposal.
As such no observable has been widely accepted as being highly representative of this multi-dimensional data,
  which severely limits their applicability in practical data processing applications.
From an alternative approach, a few POLSAR discrimination measures have been proposed,
  but all are based on the likelihood ratio statistics.
This statistical test should be based on an exact and consistent statistical distribution
  but so far has only shown to be based on an asymptotic distribution.

%Research Objective: Give your precise problem statement  
This article hence presents a scalar and representative observable, and its associated generic statistical model to describe multi-dimensional POLSAR data and provide a consistent foundation for the derivation of POLSAR discrimination measures.
%Now State your approach  
%This study started off with the observation that the determinant of the covariance matrix is widely used in POLSAR discrimination measures.
%However, our survey of existing scalar models for POLSAR indicates that no statistical model for this observable has been published so far.
%Consequently, in this article, the statistical behaviour of the determinant of POLSAR covariance matrix is further investigated.
%Prof Vuns: comment: the article provides the result, not the journey!
POLSAR data have been statistically modelled as following the complex Wishart distribution.
Consequently, the generic statistical model for the covariance matrix determinant is presented as being just a scalar projection of the multidimensional data.
This model is then used to derive several scalar and consistent statistical descriptions suggesting that their associated observables are capable of being used as discrimination measures for POLSAR data.
%
%***IVM: the following sentence doesn't make sense, also, I don't think it's good to talk about 'models of a model'.  Maybe 'model variants' instead?
%%%***IVM***The specific two and three dimensional models of these models, which %also include the derived discrimination measures, are originally designed against both partial and full polarimetric SAR data.

%The specific two and three dimensional models are then validated against both partial and full polarimetric SAR data.
Interestingly the paper also shows that %It is also shown that
  the specific one dimensional versions of the proposed  models 
  match perfectly with the traditional statistical model used for SAR intensity.
This effectively incorporates the common one dimensional SAR theory under the unbrella of the proposed scalar approach for multi dimensional POLSAR.
With this new insight the different discrimination proposals for SAR and POLSAR are reviewed and it is shown that the approach proposed in this paper provides a strong, unifying and consistent foundation relating them all together.
The applicability of these theoretical models will be illustrated by experiments where the specific one, two and three dimensional versions of the proposed generic models are validated against practical data. 
%Furthermore, the approach proposed in this paper
%  not only provides a consistent foundation for the different discrimination measures proposal in POLSAR
%  but also leads to the establishment of a new discriminating measures: the determinant-ratio and the change-ratio.

@@

%Article Organization: Show that you deliver on the objectives and hence solve the stated problem
The remainder of this article is organized as follows.
After the next section reviews existing discrimination measures as well as scalar observables models for POLSAR, section \ref{sec:theoretical_model}
  derives the generic statistical model for the determinant of the POLSAR covariance matrix
  and proposes several new discrimination measures for the multi-dimensional data.
After section \ref{sec:sar_special_case_of_polsar} illustrates the match between the specific model of one dimensional and the traditional model for SAR intensity,
  section \ref{sec:link_sar_polsar} links the disparate discrimination measure proposals for the traditional SAR and the more recent POLSAR data.
%Section \ref{sec:polsar_models_validation} then validates the specific one, two and three dimensional versions of the proposed model against real-life captured data.
The applicability of these models against practical data is illustrated in section \ref{sec:polsar_models_validation}.
Section \ref{sec:discussion} presents a high-level discussion of the results presented before
  section \ref{sec:conclusion} finally concludes the paper.

@@

%This section outlines related publication.
Section \ref{sec:lit_models} reviews various statistical models used for different scalar observables for POLSAR.
  where it is shown that none are able to provide statistically consistent discrimination measures. 
Section \ref{sec:lit_measures} further strengthens those findings by discussing discrimination measures that have been proposed for POLSAR,
  and demonstrates that almost all of them are based on the likelihood statistical test for complex Wishart distribution.
While an exact statistical distribution is expected to be necessary for a test,
  only an asymptotic distribution is used in the underlying approach \cite{Conradsen_2003_TGRS_4}.

@@

The commonly used measure of distance for matrices are either the Euclidean or Manhattan distances, defined respectively as:
\begin{align}
  d(C_x,C_y) &= \sum_{i,j} |\mathbb{R} (C_x - C_y)_{i,j}| + \sum_{i,j} |\mathbb{I} (C_x - C_y)_{i,j}| \\
  d(C_x,C_y) &= \sqrt{\sum_{i,j} |C_x - C_y|_{i,j}^2 }
\end{align}
where $C_{i,j}$ denotes the $(i,j)$ elements of the POLSAR covariance matrix C,
 $||$ denotes absolute values
and $\mathbb{R},\mathbb{I}$ denote the real and imaginary parts respectively.
However, in the context of POLSAR, % covariance matrix
  these dissimilarity measures are not widely used 
  mainly due to the multiplicative nature of the noisy data.

@@

Taking the log-transformation of the above equation, and denoting $C_{vx} = Z_x / L_x$, $C_{vy} = Z_y / L_y$ and $C_{vxy} = (Z_x + Z_y)/(L_x + L_y)$ then:
{\small
\begin{align}
  Q &= \frac{|C_{vx}|^{L_x} \cdot |C_{vy}|^{L_y} }{|C_{vxy}|^{L_x + L_y}} \label{eqn:ori_likelyhood_stats} \\
  \ln Q &= L_x \ln |C_{vx}| + L_y \ln |C_{vy}| - (L_x + L_y) \ln |C_{vxy}| \label{eqn:log_likelyhood_stats}
\end{align}
}

@@

%In this section, the generic scalar statistical model for POLSAR is presented.
In this section, after the basic foundations of POLSAR statistical analysis are introduced,
  the generic scalar statistical model for the multi-dimensional POLSAR will be presented.
%  this section presents the theoretical model for multi-dimensional POLSAR data.

@@

Moreover, since the average and variance of these chi-squared distributions %and log-chi-squared distribution
  are known to be constant, i.e. $avg \left[ \chi(2L) \right] = 2L$ and $var \left[ \chi(2L) \right] = 4L$,
  the product and summation of these random variables also have fixed summary statistics.
Specifically:
{\footnotesize
\begin{align*}
  avg \left[ \prod^{d-1}_{i=0} \chi(2L-2i) \right] &= 2^d \cdot \prod^{d-1}_{i=0} (L-i), \\
  var \left[ \prod^{d-1}_{i=0} \chi(2L-2i) \right] &= \prod^{d-1}_{i=0} 4(L-i)(L-i+1) - \prod^{d-1}_{i=0} 4(L-i)^2, %\\
%  avg \left[ \sum^{d-1}_{i=0} \Lambda(2L-2i) \right] &= d \cdot \ln{2} + \sum^{d-1}_{i=0} \psi^0(L-i), \\
%  var \left[ \sum^{d-1}_{i=0} \Lambda(2L-2i) \right] &= \sum^{d-1}_{i=0} \psi^1(L-i)
\end{align*}
}

@@

%Assuming, on the one hand,
For cases where the true value of the underlying signal $\Sigma_v$ is known \textit{a priori},
then the determinant-ratio of the signal random variable ($\mathbb{R}_{\Sigma}$) %and log-distance ($\mathbb{L}$)
%  are observable according to the following definitions:
  is defined as:
%Eqns. \ref{eqn:prod_chi_squared_rv} and \ref{eqn:sum_log_chi_squared_rv} lead straight to the definition of the following random variables, which is the :
\begin{eqnarray}
  \mathbb{R}_{\Sigma} &=& \frac{|C_v|}{|\Sigma_v|} \label{eqn:determinant_ratio_observables}%\\
%  \mathbb{L} &=& \ln|C_v| - \ln|\Sigma_v| \label{eqn:log_distance_observables} 
\end{eqnarray}
%On the other hand, under a looser assumption %From another perspective
For cases where the POLSAR data is known to have come from a homogeneous area, but the true value of the underlying signal $\Sigma_v$ is \textit{unknown},
 then a random variable called the change-ratio ($\mathbb{R}_{C}$)  is defined as:
\begin{eqnarray}
  \mathbb{R}_{C} &=& \frac{|C_1|}{|C_2|} \label{eqn:determinant_ratio_samples_observables}%\\
%  \mathbb{L} &=& \ln|C_v| - \ln|\Sigma_v| \label{eqn:log_distance_observables} 
\end{eqnarray}
where $C_1$ and $C_2$ are samples of the covariance matrix determinant in an assumed homogeneous area.

@@

Since each elementary component follows fixed distributions (i.e. $\chi^2(2L)$),
  it is natural that this variable also follows fixed distributions.
Moreover, it is independent of the underlying signal $\Sigma_v$,
  indicating its statistically consistent properties and hence its applicability as a POLSAR discrimination measure.
This claim is extrapolated from the widely-used intensity-ratio as a SAR discrimination measure
  and will be further discussed in the next sections.
%is further strengthened in the next section which shows that the generic models for POLSAR presented in this paper also include the commonly-used models for SAR as its special 1-dimensional case. 
%This result shows how
%In short, these random variables are shown to follow consistent and fixed distributions,
%  regardless of the underlying signal $\Sigma_v$.

@@

%The previous sections have introduced and validated the theoretical models for 3-dimensional ($d=3$) full polarimetric and 2-dimensional ($d=2$) partial polarimetry, cases.
This section shows that the proposed generic model is equally  applicable to the 1-dimensional ($d=1$) case,
  which is physically equivalent to  collapsing the multi-dimensional POLSAR dataset  into conventional single dimensional SAR data.
Mathematically, the sample covariance matrix $C_v$ is reduced to the sample variance while the determinant $|C_v|$ is equivalent to  the scalar variance value.
As variance is equal to intensity $I$ for SAR data, our result is consistent with previous results for SAR intensity data.
Thus the proposed generic model for POLSAR, collapsed into one dimension will be shown to map to the traditional model for SAR intensity in its natural coverage.
%****IVM: Hai, by "natural coverage" above do you mean non-built-up areas, or are you using this as a figure of speech?  Note: this sentence needs additional correction to include the word 'confidence'.. I'll do that once you can confirm the meaning of 'natural coverage'.
%  as well as reminding us that SAR is a special case of POLSAR.

@@

Since the PDF of chi-squared distribution can be written as:
\begin{align*}
\chi(2L) \sim pdf \left[ \frac{\chi^{L-1}e^{-\chi/2}}{2^L\Gamma(L)} \right]
\end{align*}
Applying variable change theorem into the above equations results in:
\begin{align*}
  |C_v| &\sim  pdf \left[ \frac{L^L x^{L-1} e^{-Lx/|\Sigma_v|}}{\Gamma(L) |\Sigma_v|^L} \right] \\ %\label{eqn:determinant_distribution} %\\
  \mathbb{R}_{\Sigma} = \frac{|C_v|}{|\Sigma_v|} &\sim pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx}}{ \Gamma(L)} \right] \\ %\label{eqn:polsar_ratio_det_cov_dist} \\
  \mathbb{R}_{C} = \frac{C_1}{C_2} &\sim pdf \left[ \frac{\Gamma(2L-1) x^{L-1}}{\Gamma^2(L-1) (1+x)^{2L}} \right]
\end{align*}
These equations match exactly with the following traditional model for multi-look SAR intensity:
  \begin{eqnarray}
I &\sim& pdf \left[ \frac{L^L x^{L-1} e^{-Lx/\bar{I}}}{\Gamma(L) \bar{I}^L} \right] \\
\mathbb{R}_{\bar{I}} = \frac{I}{\bar{I}} &\sim& pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx}}{ \Gamma(L)} \label{eqn:multi_look_SAR_ratio_dist} \right] \\
  \mathbb{R}_{I} = \frac{I_1}{I_2} &\sim& pdf \left[ \frac{\Gamma(2L-1) x^{L-1}}{\Gamma^2(L-1) (1+x)^{2L}} \right]
  \end{eqnarray}
considering that $|C_v| \mapsto I$ and $|\Sigma_v| \mapsto \bar{I}$ as multi-dimensional POLSAR collapses into single-dimensional SAR.

@@

Statistical models have always been the foundation for deriving discrimination measures.
This is true for both fields of SAR and POLSAR.
For SAR, where the field is more or less settled on the issue,
  the statistical model for SAR intensity has been used to derive the most widely used intensity-ratio discrimination measure \cite{Rignot_1993_TGRS_896}.
For POLSAR, where the research field is much less mature,
  the same case should apply, 
  except that so far only asymptotic distributions have been derived for the most common foundation, i.e. the likelihood test statistics \cite{Conradsen_2003_TGRS_4}.

@@

As for the first matter, in view of the models given in Eqn \ref{eqn:determinant_distribution},
  the likelihood test statistics presented in \cite{Conradsen_2003_TGRS_4} and rewritten in Eqns \ref{eqn:ori_likelyhood_stats} \& \ref{eqn:log_likelyhood_stats}
can be expressed as:
\begin{align*}
  \ln{Q} &\sim  k + L_x \Lambda^d_{L_x} + L_y \Lambda^d_{L_y} - (L_x + L_y) \Lambda^d_{(L_x + L_y)} \\
  Q &\sim e^k \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y}}{(\chi^d_{L_x + L_y})^{L_x + L_y}}   
\end{align*}
where $k = d \left[ (L_x + L_y) \ln(L_x + L_y) - L_x \ln{L_x} - L_y \ln{L_y} \right]$.
This, in essence, derives an exact statistical distribution for the likelihood test statistics,
  as opposed to the asymptotic distribution derived in \cite{{Conradsen_2003_TGRS_4}}.

@@

Since it has been shown in Section \ref{sec:sar_special_case_of_polsar} that the model for the case of $d=1$ matches exactly with the traditional model for SAR intensity,
  the validation of the proposed $d=1$ model is quite straightforward. %only a simple validation is presented for this case.  
Fig. \ref{fig:verify_POLSAR_model_1D} presents the results of a test performed for the stated purpose.
In the test, the intensity of single-channel SAR data (HH) for sample homogeneous areas in both datasets is extracted.
The histograms for both the intensity and intensity ratio %the log-distance and contrast
  are then plotted against the theoretical PDF given above.
%Also presented are the plots of the same test applied on a homogeneous patch inside the nine-look processed RADARSAT2 image.
The plots are obtained having set ENL to an estimated value obtained using the technique presented in \cite{Anfinsen_2009_TGRS_3795}.
In all cases, the good visual match between the actual data and model distribution tends to validate the proposed model. %providing us a simple validation of the result.
